There are no small Advantages: Reinforcement learning in near continuous time with Deep RelAtive Mixture of Advantages

### 2019-01-10 paper/icml_drau/advup.tex
sec:continuous => sec:framework

\section{Deep Advantage Updating}
In continuous time, $Q^\pi$ is independant of actions and can thus not be used
to select promising actions.  In near continuous time, $Q^\pi$ still depends on
actions, and can still be used to choose promising actions under the current
policy. However, when approximating $Q^\pi$, if the approximation error is much
bigger than $\bigO(\deltat)$, approximation errors dominates, and the hierarchy
of actions given by the approximation is likely to be erroneous.

When the approximate Q-function is initialized, if the effect of actions on the
Q-function is order of magnitudes higher than what it should be, approximating
$Q^\pi$ is likely to be difficult. Besides, the error is likely to be further
propagateed when the equation used to update our approximate $Q$ function
relies on bootstraping, as is the case for usual temporal difference derived methods.

>>>>

%! TEX root = icml_drau.tex
\section{Reinforcement learning with a continuous time limit}
As seen in Sec.~\ref{sec:framework}, there is no continuous time limit to
Q-learning. In continuous time, $Q^\pi$ is independant of actions and can thus
not be used to select promising actions.  In near continuous time, $Q^\pi$
still depends on actions, and can still be used to choose promising actions
under the current policy. However, when approximating $Q^\pi$, if the
approximation error is much bigger than $\bigO(\deltat)$, approximation errors
dominates, and the hierarchy of actions given by the approximation is likely to
be erroneous.
When the approximate Q-function is initialized, if the effect of actions on the
Q-function is order of magnitudes higher than what it should be, approximating
$Q^\pi$ is likely to be difficult. Besides, the error is likely to be further
propagated when the equation used to update our approximate $Q$ function
relies on bootstraping, as is the case for usual temporal difference derived methods.
